The evolution of the transcriptome of mammalian placentas

### 2016-09-19 manuscript/manuscript.Rnw
rewrite starting introduction paragraph

The placenta is arguably one of the most variable organs in different
species of mammals in terms of the shape of attachment
(\Sexpr{english.join(placenta_classification[,levels(as.factor(shape))])}),
degree of intimacy between fetal tissues and maternal tissues
(\Sexpr{english.join(placenta_classification[,levels(as.factor(intimacy))])}),
and degree of interdigitation of maternal and fetal tissues
(\Sexpr{english.join(placenta_classification[,levels(as.factor(interdigitation))])})
while its primary functions (transfer of nutrients and oxygen to the
fetus, removal of wastes and carbon dioxide) are strongly conserved.

Even though the placenta's primary function is conserved among

>>>>

Even though the placenta's primary function is conserved among
mammals, it varies widely in terms of the shape of attachment, degree
of intimacy between fetal tissues and maternal tissues and degree of
interdigitation of maternal and fetal tissues in different species of
mammals
\cite{Mossman.1987:vertebratefetalmembranes,Moffett.ea2006:Immunologyofplacentationin}
(Supplemental \cref{tab:placental_classification}). Mammals also
differ drastically in the number and size of their offspring, as well
as the length of gestation; these traits are often with specific
aspects of placental morphology
\cite{Capellini.ea2011:Placentationandmaternalinvestment}
(Supplemental \cref{tab:gestational_periods}).
